Towards a classification framework for social machines

### 2013-02-21 latex/paper_new.tex
related work section

>>>>

A Social Machine includes human and machine two major components, therefore, the study of social machine is an interdisciplinary endeavour. Since the Turning machine was invented, there has been a `paradigm shift' in using computers, where the computer facilitates human communication rather acts as a purely calculative device. The Computer-supported Collaboration Work (CSCW) emerged in 1982 represent such shift. It addresses ``how collaborative activities and their coordination can be supported by means of computer systems'' later evolved in a more broader sense of  Computer-supported collaboration (CSC). The Social computing is another shift, which is a generic term refers systems that support ``the gathering, representation, processing, use, and dissemination of information that is distributed across social collectivities such as teams, communities, organizations, and markets''. To compare with the CSC, the social computing has more focus in computing rather than broader sense of

CSCW (1982)	"how collaborative activities and their coordination can be supported by means of computer systems."

Social Computing (1994)	the system that support the gathering, representation, processing, use, and dissemination of information that is distributed across social collectivities such as teams, communities, organizations, and markets.

Open Innovation (2003)	Paradigm in how companies commercialize trial knowledge.

Is a paradigm that assumes that firms can and should use external ideas as well as internal ideas, and internal and external path to market, as the firms look to advance their technology. It combines internal and external ideas into architectures and systems whose requirements are defined by a business model. 
The Wisdom of Crowds (2004)
	About the aggregation of information in groups, resulting in decisions that, he argues, are often better than could have been made by any single member of the group. 
Human Computation (2005)	.	“...a paradigm for utilizing human processing power to solve problems that computers cannot yet solve.”

Crowdsourcing (2006)	“Crowdsourcing is the act of taking a job traditionally
performed by a designated agent (usually an employee) and outsourcing it to an undefined, generally large group of people in the form of an open call.”
.	
Collective Intelligence (2009)	"... groups of individuals doing things collectively that seem intelligent.”

The Wisdom of Crowds described by Surowiecki, It is idea of the aggregation of information in groups, resulting in decisions that are often better than could have been made by any single member of the group.

The Open Innovation also describe the similar idea on how companies commercialise trial knowledge - instead of only use internal ideas, it should also use external ideas to advance their technology.
